### 2019-05-26 doc/chapters/introduction.tex
End of Bincoin-S in introduction.tex

@@

In the work some fragments of the code of Bitcoin-S will be verified. Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S. Protocol data structures are defined in the package \textbf{bitcoin-s-core}. This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is a RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.

%\begin{itemize}
%	\item Create a BFH Style Files
%	\item Template for the Compilation of presentations with \LaTeX{}
%\end{itemize}

>>>>

The code being verified with Stainless should be written in Pure Scala, that corresponds to the functional programming. But also some imperative features are supported by Stainless.

@@

In the work some fragments of the code of Bitcoin-S has to be verified. Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S. Protocol data structures are defined in the package \textbf{bitcoin-s-core}. This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is a RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
The whole list of packages can be found on the github \cite{BitcoinSProject}.

Bitcoin-S is a large project implementing many functionalities. In this work one of them is going to be examinated and worked on, namely the property of the Bitcoin that a non-coinbase transaction can not generate new coins.
Thus, the code of Bitcoin-S should be analyzied, and fragments implementing this feature should be identified.
Afterwards, the fragments should be rewritten, so that Stainless can accept it. After that a formal specification for functions should be defined and annotated according Stainless libraries, so that Stainless can verify corrrectness of the code.
